History of Social Work Research: Data Cleaning

### 2015-02-04 dataCleaning.Rmd
Updated R objects.

```{r}
years <- c("2014", "2015")
ebsco.remove <- full.df[full.df$record %in% years, ]
ebsco.remove <- ebsco.remove[, "articleID"]
full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]

range.of.years <- range(full.df$record[full.df$attributes == "pubYear"])

# New range of years
cat(range.of.years)
```

@@

```{r exclusion1, eval=TRUE}
exclusions.1 <- c(
    "American Journal of Preventive Medicine", 
    "Behavior Modification", 
    "Brain and Cognition",
    "Canadian Journal of Community Mental Health",
    "Canadian Journal on Aging",
    "Early Child Development and Care",
    "Early Education and Development",
    "Employee Assistance Quarterly",
    "Evaluation and Program Planning",
    "General Hospital Psychiatry",
    "International Review of Social Research",
    "Journal of Applied Behavioral Science",
    "Journal of Applied Rehabilitation Counseling",
    "Journal of Applied Social Sciences",
    "Journal of Community & Applied Social Psychology",
    "Journal of Health & Human Services Administration",
    "Journal of Nonverbal Behavior",
    "Journal of Psychosomatic Research",
    "Learning Disabilities Research & Practice",
    "New York State Department of Social Welfare, Division Publication",
    "Proceedings of the National Converence of Social Work",
    "PROFILE Issues in Teachers' Professional Development",
    "Psychotherapy",
    "Systems Research and Behavioral Science",
    "Teaching and Teacher Education",
    "University of Chicago Social Service Monograph",
    "The Scientific Review of Mental Health Practice",
    "The Clinical Supervisor")

@@

rm(ebsco.remove, exclusions.1)
```

@@

```{r exclusion2, eval=TRUE}
exclusions.2 <- c(
    "Eugenics and Social Welfare Bulletin",
    "Eugenics & Social Welfare Bull.",
    "Issues in Social Work Education", 
    "Hospital Social Service",  #Confirmed nursing journal
    "International Conference of Social Work",
    "Journal of Multicultural Social Work",
    "Journal of Teaching in Social Work", 
    "Maatskaplike Werk/Social Work",
    "Medical Social Work",
    "New York State Department of Social Welfare, Division Publication",
    "Pediatric Social Work", 
    "Pennsylvania Social Work",
    "Social Service",    
    "Social Service Department, Presbyterian Hospital, New York",
    "Social Service Monographs",
    "School Social Work Quarterly", # Published only one edition
    "Social Work Today",
    "Social Work Technique",
    "Social Work Today", # Magazine
    "Social Work Yearbook",
    "The New Social Worker",
    "Pennsylvania Social Work",
    "University of Chicago Social Service Monograph" # Single record
    )

@@

```{r titleMerge, eval=TRUE}
full.df$record <- ifelse(full.df$record == "The British Journal of Social Work", 
                       "British Journal of Social Work", 
                        full.df$record)

full.df$record <- ifelse(full.df$record == "Social Work & Social Sciences Review", 
                       "Social Work and Social Sciences Review", 
                        full.df$record)

full.df$record <- ifelse(full.df$record == "Social Work with Groups", 
                       "Social Work With Groups", 
                        full.df$record)

full.df$record <- ifelse(full.df$record == "Computers in Human Services", 
                       "Journal of Technology in Human Services", 
                        full.df$record)

full.df$record <- ifelse(full.df$record == "Journal of Sociology & Social Welfare", 
                       "Journal of Sociology and Social Welfare", 
                        full.df$record)

full.df$record <- ifelse(full.df$record == "The Family", 
                       "Families in Society",
                       ifelse(full.df$record == "Journal of Social Casework",
                       "Families in Society",
                       ifelse(full.df$record == "Social Casework",
                       "Families in Society",
                        full.df$record)))

full.df$record <- ifelse(full.df$record == "Social Work in Education", 
                       "Children & Schools", 
                        full.df$record)
```

@@

names(full.df)

>>>>

```{r}
years <- c("2014", "2015")
ebsco.remove <- full.df[full.df$record %in% years, ]
ebsco.remove <- ebsco.remove[, "articleID"]
full.df <- full.df[!(full.df$articleID %in% ebsco.remove),]
```

@@

```{r exclusion1, eval=TRUE}
exclusions.1 <- c(
    "American Journal of Preventive Medicine", 
    "Behavior Modification", 
    "Brain and Cognition",
    "Canadian Journal of Community Mental Health",
    "Canadian Journal on Aging",
    "Early Child Development and Care",
    "Early Education and Development",
    "Employee Assistance Quarterly",
    "Evaluation and Program Planning",
    "General Hospital Psychiatry",
    "International Review of Social Research",
    "Journal of Applied Behavioral Science",
    "Journal of Applied Rehabilitation Counseling",
    "Journal of Applied Social Sciences",
    "Journal of Community & Applied Social Psychology",
    "Journal of Health & Human Services Administration",
    "Journal of Nonverbal Behavior",
    "Journal of Psychosomatic Research",
    "Learning Disabilities Research & Practice",
    "New York State Department of Social Welfare, Division Publication",
    "Proceedings of the National Conference of Social Work",
    "PROFILE Issues in Teachers' Professional Development",
    "Psychotherapy",
    "Social Service Department, Presbyterian Hospital, New York",
    "Social Work Technique", 
    "Social Work Today", 
    "Social Work Yearbook", 
    "The New Social Worker",
    "Systems Research and Behavioral Science",
    "Teaching and Teacher Education",
    "University of Chicago Social Service Monograph",
    "The Scientific Review of Mental Health Practice",
    "The Clinical Supervisor",
    "University of Chicago Social Service Monograph")

@@

rm(ebsco.remove)
```

@@

```{r exclusion2, eval=TRUE}
exclusions.2 <- c(
    "Eugenics and Social Welfare Bulletin",
    "Eugenics & Social Welfare Bull.",
    "Issues in Social Work Education", 
    "Hospital Social Service",  #Confirmed nursing journal
    "International Conference of Social Work",
    "Journal of Multicultural Social Work",
    "Journal of Social Work Process",
    "Journal of Teaching in Social Work", 
    "Maatskaplike Werk/Social Work",
    "Medical Social Work",
    "New York State Department of Social Welfare, Division Publication",
    "Pediatric Social Work", 
    "Pennsylvania Social Work",
    "Social Service",    
    "Social Service Department, Presbyterian Hospital, New York",
    "Social Service Monographs",
    "School Social Work Quarterly", # Published only one edition
    "Social Work Today",
    "Social Work Technique",
    "Social Work Today", # Magazine
    "Social Work Yearbook",
    "The New Social Worker",
    "Pennsylvania Social Work",
    "University of Chicago Social Service Monograph" # Single record
    )

@@

```{r titleMerge, eval=TRUE}
full.df$record <- ifelse(full.df$record == 
        "The British Journal of Social Work",       # Old title
        "British Journal of Social Work",           # New title
                        full.df$record)

full.df$record <- ifelse(full.df$record == 
        "Social Work & Social Sciences Review",     # Spelling difference
        "Social Work and Social Sciences Review", 
                        full.df$record)

full.df$record <- ifelse(full.df$record == 
        "Social Work with Groups",                  # Spelling difference
        "Social Work With Groups", 
                        full.df$record)

full.df$record <- ifelse(full.df$record == 
        "Computers in Human Services",              # Old title
        "Journal of Technology in Human Services",  # New title
                        full.df$record)

full.df$record <- ifelse(full.df$record == 
        "Journal of Sociology & Social Welfare",    # Spelling difference
        "Journal of Sociology and Social Welfare",  
                        full.df$record)

full.df$record <- ifelse(full.df$record == 
        "The Family" | full.df$record ==                    # Old title
        "Journal of Social Casework" | full.df$record ==    # Old title
        "Social Casework",                                  # Old title
        "Families in Society",                              # New title
                        full.df$record)

full.df$record <- ifelse(full.df$record == 
        "Social Work in Education",                 # Old title
        "Children & Schools",                       # New title
                    full.df$record)
```

@@
